\textbf{Supplementary Materials}\\ A Critical Appraisal of the Zero-Multiple Method: Structural, Thermodynamic, Dielectric, and Dynamical Properties of a Water System

### 2014-11-13 writedown/zm/paper.water/main.tex
my revise

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
\input{tcilatex}
\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\author{Haruki Nakamura}
\date{\today}

@@

\maketitle
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? {\color{red} I mean the explanation of group and atomistic
cut-off method. the traditional gromacs uses gropu cut-off as default. We
need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
If we feel the resulted descriptions are too detailed, they will go to SI.}] 
}

@@

The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
order to mimic the atomistic cut-off manner, the radius for neighbor list
building was set 0.3~nm larger than the cut-off radius (the maximum of
Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}] To
make sure the van der Waals interactions were cut-off in a smooth way, they
are modified in a shell of $0.05$~nm width near the cut-off sphere by the
Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.

The short-range part of SPME method {\color{red} was cut-offed at 1.9~nm,
and was}[ {\color{blue} OK] }smoothed in a shell of $0.05$~nm width by the
Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
reciprocal space grid spacing was set to 0.06~nm, with B-Spline
interpolation order of 6. These parameters were chosen to be more accurate
than the Gromacs default choices (grid spacing 0.12~nm and interpolation
order 4). The splitting parameter was optimized by the error estimate for
the SPME method, which is implemented in Gromacs by tool \textquotedblleft 
\texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
optimized real space and reciprocal space force computing errors were
equally distributed as $1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude
of the forces are of order $10^{2}$~kJ/(mol nm), this force computing
precision almost reaches the limit of the single-precision representation of
the floating point numbers. [ {\color{blue} COMMENT: Did you use the
conducting boundary conditions? (maybe it is default in gromacs.) Please
state the thing.}]

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm cut-off and the
experimental dielectric constant $\varepsilon _{\text{rf}}=80$.

@@

@@

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$ were
used as initial configurations for system $S_{1}$ and $M_{1}$, respectively.
The final configuration of $L_{1}^{\prime }$ was used as initial
configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with SPME electrostatic, the
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
which means the system is in desired thermodynamic state. [ {\color{blue}
COMMENT: If there are any specific conditions only for the pressure
calculation, please state around here or elsewhere.] }

@@

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZM results on the order\ $l$\ is {\color{red}
little}. Although the splitting parameter, $\alpha $, also does not have
significant influence on almost all these thermodynamic quantities for $l=1$%
, only the isothermal compressibility admits a weak dependence [{\color{red}
all except $\alpha =2$ are in the statistical uncertainty, by which we
cannot say $\alpha =1$ is optimal... I remove \textquotedblleft and $\alpha
=1$ seems optimal\textquotedblright } {\color{blue} OK}]. Overall, the ZM\
agrees with the SPME results without any bias and out-performs the RF.

@@

{\color{red} It should be noted that even with the system $L_{0}$ that
contains 13824 water molecules[} {\color{blue} OK}], the fluctuation
(measured by standard deviation) of the pressure is roughly 100~Bar, which
means that it is very difficult to achieve very accurate estimate for this
quantity. In practice a pressure error of 20~Bar is still acceptable.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
and not shown in your report. right? }]}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite%
{vanderSpoel2006origin}, therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM
shows good results without any {\color{red} system-size dependency} {[} {%
\color{blue} OK}]and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
the accuracy. Since a slow convergence is also known for the dielectric
constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv}%
, and confirm the sufficient convergence w.r.t.~the length of the
trajectories. {%
\color{red} [COMMENT: the system size and cut-off dependency
  are important,
  but since the result are consistent with system $S_1$ and rc=1.2~nm (shown in table II),
  and NO new phenomenum is observed, 
  they are put in SI.]\lbrack } {\color{blue} OK}]

@@

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
method is qualitatively wrong, and the accuracy of the ZM method is much
higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
highly consistent with the SPME result, and $l=2$ seems the best. In the
system of larger size ($L_{1}$), the accuracies of the ZM method is less for
order $l\geq 2$, while they may be in still acceptable accuracy. In both
systems, ZM $l=1$ presents an artificial oscillation around the cut-off
radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$.

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps}
\caption{ The splitting parameter dependency in calculating the Kirkwood-G
factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
\color{blue} This is also not shown in your report. right? }]}
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
. Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius. {\color{red} In Fig.~\ref%
{fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
Kirkwood-G factor than smaller splitting parameters.[} {\color{blue} OK}]
Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
SI). Note that in many cases the discrepancies from the SPME were relatively
prominent in the middle range of the distance and they tend small for larger
distance.

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about $2\%$,{[} {\color{blue}
"$2\%"$ is just my guess. How about stating here the maximum error for
individual $l$}] but should be artificial. However, higher order ZM method
present lower amplitude oscillation, and when $l\geq 3$, the improvement is
dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material {\color{blue} Do you
mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
it? or it is too complicated and not very relevant to the current paper?}[} {%
\color{blue} It is preferable to write it if the reason of the goodness is
clear. Anyway, please describe.... This is the only matter ZM is inferior to
RF. So, it may be interesting if the reason is clear. }]

@@

In summary, ZM works well for almost all cases. Damping effect of the
splitting parameter, viz., larger $\alpha $\ gives accurate results, was
seen in several quantities. The weak effect is seen in the isothermal
compressibility, {\color{red} } and dynamical quantities including the
diffusion constant and viscosity, while the strong effect is seen in the
RDF. Anti-damping effect was also observed in the pressure when $\alpha >1$
and  {\color{blue}Kirkwood-G factor (only $l=1$).[ OK??}] A larger order is
preferable slightly for dynamical quantities including diffusion constant
and viscosity, and significantly for the RDF. Whereas a smaller order is
preferable for the pressure, though $l=1,2$\ are similar.

{\color{red} At cut-off radius of 1.2~nm, the recommended choices of
parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
accuracy in computing the excess chemical potential, constant
volume/pressure heat capacity, isothermal compressibility, thermal expansion
coefficient, dielectric constant diffusion constant and viscosity. The order 
$l=2$ performs better in reproducing the pressure than $l=3$ (10
v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
negligible). Both of orders 2 and 3 are not sensitive to the splitting
parameter up to 1.0~$\text{nm}^{-1}$.} {\color{blue} Although further
increasing the splitting parameter will push the accuracy of RDF in case $l=2
$ to as high as $l=3$, the pressure accuracy decreases (anti-damping
effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
should be noticed that the recommended parameters indicate $5$\% error
(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
containing 13,824 molecules). [\color{blue}COMMENT:Did you calculate the G
factor for the smallest $S_{1}$? \ If so, how was the results?] If we seek
more accuracy for the G factor, we should use a larger cut-off radius at the
expense of the computational time. } 
% Further increasing the splitting paraemter
% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
% where the error about $0.2\%$\  remains in the RDF. An
% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
% not the best but highly accurate RDF can be obtained.

@@

The pressure of the system calculated by the virial formula:[ {\color{blue}
Modified $3N\longrightarrow N$} {\color{red} should be $3N$!, each molecule
contains 3 atoms. The pressure is computed by atom based virial formula. %
\color{blue} OK, I was just confusing}]%
\begin{equation*}
P=\frac{1}{3V}\Bigg\langle\sum_{i=1}^{3N}\Big(m_{i}\mathbf{\mathit{v}}%
_{i}^{2}+\mathbf{\mathit{r}}_{i}\cdot \mathbf{\mathit{F}}_{i}\Big)%
\Bigg\rangle,
\end{equation*}%
where $V$ is the volume of the system. The presented pressures were computed
in system $L_{0}$.

@@

\bibliographystyle{plain}
\bibliography{ref}
{}

>>>>

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\exc}{\textrm{ex}}
\newcommand{\systemsa}{S_0}
\newcommand{\systemsb}{S_1}
\newcommand{\systemsbp}{S'_1}
\newcommand{\systemma}{M_0}
\newcommand{\systemmb}{M_1}
\newcommand{\systemmbp}{M'_1}
\newcommand{\systemla}{L_0}
\newcommand{\systemlbp}{L'_1}
\newcommand{\systemlb}{L_1}
% \input{tcilatex}
\begin{document}

\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}

\date{\today}

@@

\maketitle

@@

{\color{red} If we want to discuss the issue of cut-off method, a short
introduction of the group cut-off v.s.~the atom cut-off method. (will
discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
do you mean? {\color{red} I mean the explanation of group and atomistic
cut-off method. the traditional gromacs uses gropu cut-off as default. We
need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
If we feel the resulted descriptions are too detailed, they will go to SI.}] 
}
[\recheck{please see the red part in Sec. III B. The order of the paragraphs are also rearranged.}]

@@

The neighbor lists were updated every 5 time-steps.
\recheck{The Gromacs by default uses the group cut-off scheme, while the ZM method suggests
  an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between
  these cut-off schemes is discussed in detail in e.g.~Ref.~\cite{hunenberger1998alternative,baumketner2009removing}.
  We adopted the atom based cut-off scheme in the simulations using the
  SPME (short-range part) and ZM electrostatic methods.
  In order to mimic the atom cut-off scheme in the Gromacs group cut-off implementation,
  the radius for neighbor list
  updating was set 0.3~nm larger than the cut-off radius (the maximum of
  Coulomb cut-off and the van der Waals cut-off). 
}

% The \textquotedblleft 
% \texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used.[ {\color{blue} COMMENT:
% Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
%   should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}]

The short-range part of SPME method was cut-offed at 1.9~nm,
and was smoothed in a shell of $0.05$~nm width by the
Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
reciprocal space grid spacing was set to 0.06~nm, with B-Spline
interpolation order of 6. These parameters were chosen to be more accurate
than the Gromacs default choices (grid spacing 0.12~nm and interpolation
order 4).
\recheck{The conducting boundary condition was used with SPME.}
The splitting parameter was optimized by the error estimate, which is implemented in Gromacs by tool \textquotedblleft 
\texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
optimized real space and reciprocal space force computing errors were
equally distributed as $1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude
of the forces are of order $10^{2}$~kJ/(mol nm), this force computing
precision almost reaches the limit of the single-precision representation of
the floating point numbers.
% [ {\color{blue} COMMENT: Did you use the
% conducting boundary conditions? (maybe it is default in gromacs.) Please
% state the thing.}]

@@

In the simulations of the RF method, the interactions were cut-off in the
group manner, so the radius for neighbor list building is set identical to
the cut-off radius. No cut-off smoothing of the electrostatic interaction
was applied in the cases of RF simulations. We used $1.2$~nm cut-off radius and the
experimental dielectric constant $\varepsilon _{\text{rf}}=80$.

The van der Waals interaction was always cut-offed at 1.2~nm, and it was
modified in a shell of $0.05$~nm width near the cut-off sphere by the
Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.

@@

The initial configurations were prepared by in the following steps: (1) An
NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
calculated from this simulation. (2) Initial configurations that contains
2500, 4500 and 13824 molecules were generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system $%
S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$ were
used as initial configurations for system $S_{1}$ and $M_{1}$, respectively.
The final configuration of $L_{1}^{\prime }$ was used as initial
configurations for system $L_{0}$ and $L_{1}$. % The SPME
% parameters for all simulations reported by this work is: real space
% cut-off 1.90~nm.
% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
%   special care, please modify.}]
Using the density in the NVT simulation with SPME electrostatic, the
pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
which means the system is in desired thermodynamic state. [ {\color{blue}
COMMENT: If there are any specific conditions only for the pressure
calculation, please state around here or elsewhere.] [\recheck{No.}]}

@@

Thermodynamic quantities including, the chemical potential, constant
volume/pressure molar heat capacity, isothermal compressibility and heat
expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
are in good consistency with the SPME results. In almost all cases the
deviations from the SPME results are smaller than the statistical
uncertainty. The RF was not so bad, but the results of the constant pressure
molar heat capacity and the isothermal compressibility show considerable
errors. The dependence of the ZM results on the order\ $l$\ is {\color{red}
little}. Although the splitting parameter, $\alpha $, also does not have
significant influence on almost all these thermodynamic quantities for $l=1$%
, only the isothermal compressibility admits a weak dependence. Overall, the ZM\
agrees with the SPME results without any bias and out-performs the RF.

@@

It should be noted that even with the system $L_{0}$ that
contains 13824 water molecules, the fluctuation
(measured by standard deviation) of the pressure is roughly 100~Bar, which
means that it is very difficult to achieve very accurate estimate for this
quantity. In practice a pressure error of 20~Bar is still acceptable.

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
\caption{The dielectric constant convergence with respect to length of the
trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
and not shown in your report. right? } \recheck{Right, it was not shown}]}
\label{fig:eps-conv}
\end{figure}

The dielectric constant computed by ZM method at different orders are listed
in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
In contrast, the RF method has poor accuracy in the dielectric constant. It
is well known that the dielectric feature shows system-size dependence~\cite{vanderSpoel2006origin},
therefore we further investigated this dependence
and also the effect of the cutoff length, as shown in Table~I of SI. ZM
shows good results without any system-size dependency and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
the accuracy. Since a slow convergence is also known for the dielectric
constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
and confirm the sufficient convergence w.r.t.~the length of the
trajectories.

@@

As a measurement of the dipole correlation as a function of molecular
distance, the Kirkwood-G factor is an important quantity of the water
system. Considering the system size dependence~\cite{vanderSpoel2006origin},
we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
method is qualitatively wrong, and the accuracy of the ZM method is much
higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
highly consistent with the SPME result, and $l=2$ seems the best. In the
system of larger size ($L_{1}$), the accuracies of the ZM method is less for
order $l\geq 2$, while they may be in still acceptable accuracy. In both
systems, ZM $l=1$ presents an artificial oscillation around the cut-off
radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$.
\recheck{
  The Kirkwood-G factor computed by ZM in system $S_1$ is as good as that computed in $M_1$,
  and is presented in SI.}

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps}
\caption{ The splitting parameter dependency in calculating the Kirkwood-G
factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
\color{blue} This is also not shown in your report. right? } \recheck{Right, it was not shown.}]}
\label{fig:gkr-damp-l1}
\end{figure}

We thus investigated the cut-off dependency in calculating the Kirkwood-G
factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
. Without surprising, the Kirkwood-G factor converges to the SPME result
when using increasingly large cut-off radius. In Fig.~\ref%
{fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
Kirkwood-G factor than smaller splitting parameters.
Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
SI). Note that in many cases the discrepancies from the SPME were relatively
prominent in the middle range of the distance and they tend small for larger
distance.

@@

We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
) with $\alpha =0$\ and RF methods. It is observed from the figure that the
ZM RDFs are consist very well with the SPME RDF, except oscillations around
the cut-off radius. This oscillations are not so large, as the maximum
magnitude of the discrepancies from the SPME is about \recheck{ $1.9\%$ for $l=1$ and 0.3\% for $l=2$,}
% {[} {\color{blue}
% "$2\%"$ is just my guess. How about stating here the maximum error for
% individual $l$}]
but should be artificial. However, higher order ZM method
present lower amplitude oscillation, and when $l\geq 3$, the improvement is
dramatic and the oscillation is almost negligible.

{\color{red} Shall we comment here on the fact that group cut-off produces
smoother RDF? Add figures in Supplementary material {\color{blue} Do you
mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
it? or it is too complicated and not very relevant to the current paper?}[} {%
\color{blue} It is preferable to write it if the reason of the goodness is
clear. Anyway, please describe.... This is the only matter ZM is inferior to
RF. So, it may be interesting if the reason is clear. } \recheck{I agree, if the
reason is not clear for us, we should not touch this topic.}]

@@

In summary, ZM works well for almost all cases. Damping effect of the
splitting parameter, viz., larger $\alpha $\ gives accurate results, was
seen in several quantities. The weak effect is seen in the isothermal
compressibility, {\color{red} } and dynamical quantities including the
diffusion constant and viscosity, while the strong effect is seen in the
RDF. Anti-damping effect was also observed in the pressure when $\alpha >1$
and  Kirkwood-G factor (only $l=1$). A larger order is
preferable slightly for dynamical quantities including diffusion constant
and viscosity, and significantly for the RDF. Whereas a smaller order is
preferable for the pressure, though $l=1,2$\ are similar.

{\color{red} At cut-off radius of 1.2~nm, the recommended choices of
parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
accuracy in computing the excess chemical potential, constant
volume/pressure heat capacity, isothermal compressibility, thermal expansion
coefficient, dielectric constant diffusion constant and viscosity. The order 
$l=2$ performs better in reproducing the pressure than $l=3$ (10
v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
negligible). Both of orders 2 and 3 are not sensitive to the splitting
parameter up to 1.0~$\text{nm}^{-1}$.} {\color{blue} Although further
increasing the splitting parameter will push the accuracy of RDF in case $l=2
$ to as high as $l=3$, the pressure accuracy decreases (anti-damping
effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
should be noticed that the recommended parameters indicate $5$\% error
(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
containing 13,824 molecules). [\color{blue}COMMENT:Did you calculate the G
factor for the smallest $S_{1}$? \ If so, how was the results? \recheck{see the added
  in Sec. IV B and SI}] If we seek
more accuracy for the G factor, we should use a larger cut-off radius at the
expense of the computational time. } 
% Further increasing the splitting paraemter
% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
% where the error about $0.2\%$\  remains in the RDF. An
% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
% not the best but highly accurate RDF can be obtained.

@@

The pressure of the system calculated by the virial formula:
% [ {\color{blue}
% Modified $3N\longrightarrow N$} {\color{red} should be $3N$!, each molecule
% contains 3 atoms. The pressure is computed by atom based virial formula. %
% \color{blue} OK, I was just confusing}]%
\begin{equation*}
P=\frac{1}{3V}\Bigg\langle\sum_{i=1}^{3N}\Big(m_{i}\mathbf{\mathit{v}}%
_{i}^{2}+\mathbf{\mathit{r}}_{i}\cdot \mathbf{\mathit{F}}_{i}\Big)%
\Bigg\rangle,
\end{equation*}%
where $V$ is the volume of the system. The presented pressures were computed
in system $L_{0}$.

@@

% \bibliographystyle{plain}
\bibliography{ref}
{}

### 2014-11-13 writedown/zm/paper.water/si.tex
my revise

\title{\textbf{Supplementary Materials}\\
  A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}

@@

>>>>

\title{\textbf{Supplementary Materials}\\
  A Critical Appraisal of the Zero-Multiple Method: Structural,
Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
6, 100088 Beijing, China}
\affiliation{Zuse Institute Berlin (ZIB), Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}
\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
Saitama 351-0198, Japan}
\author{Haruki Nakamura}
\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
Osaka 565-0871, Japan}

@@

\begin{figure}[tbp]
\centering
\includegraphics[]{fig/result.nvt.tiny/fig-gkr.eps}
\caption{
  The Kirkwood G-factor calculated for system $S_{1}$.
  ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The
RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm
and dielectric constant of 80. The statistical uncertainty of the SPME
method is presented at 95~\% confidence level with the red error bars. the
statistical uncertainty of the SPME method is denoted by the red error bars.
The statistical uncertainties of the other methods are essentially of the
same size as the SPME, so they are not presented in the figure for clarity.
}
\label{fig:gkr-conv-alpha}
\end{figure}
